---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# starpolishr

This package allows for easy post polishing of latex [stargazer](https://cran.r-project.org/web/packages/stargazer/index.html)
output. See
[this vignette](https://github.com/ChandlerLutz/starpolishr/blob/master/vignettes/pdf/starpolishr-intro.pdf) for
a quick introduction. For examples, see the `Tables` section of my
papers [here](https://chandlerlutz.github.io/pdf/california-foreclosure-prevention-laws.pdf) and [here](https://chandlerlutz.github.io/pdf/local-labor-markets-canada-us.pdf). All of these tables were generated
exclusively within R using `stargazer` and `starpolishr`.

## Installation

You can install starpolishr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ChandlerLutz/starpolishr")
```

## Quick Tips

* The first argument in all `starpolishr` functions is a
`stargazer` table, allowing for easy compatibility with
the
[magrittr](https://cran.r-project.org/web/packages/magrittr/index.html) `%>%`.
* All of the functions in the `starpolishr` package begin with
`star_` for easy `tab` completion in emacs or rstudio.

## Key Functions

Here is a list of key `starpolishr` functions in order of how often I
use them. See their help files for more details.

* `star_tex_notes` -- Adds custom notes using either the
  latex [caption](https://www.ctan.org/pkg/caption) or the
  latex [threeparttable](https://www.ctan.org/pkg/threeparttable).
* `star_tex_write` -- writes latex tables to a file and optionally
  adds header files and common packages
* `star_lhs_names` and `star_rhs_names` -- updates variable names
  using regular expressions. The advantage of these functions is that
  they allow for variable names to span more than one line.
* `star_panel` -- panels multiple related `stargazer` tables into a
  single latex table.
* `star_insert_row` -- insert a row after a given row in a `stargazer`
  table
* `star_sidewaystable` -- converts a latex table to a latex
  `sidewaystable`
* `star_add_column_numbers` -- if you pass a matrix to `stargazer`, it
  won't add column numbers. This function will add column numbers to a
  latex table.


## Authors

[Chandler Lutz](https://chandlerlutz.github.io/)

## License

GPL (>= 2)
