---
title: "`starpolishr`: Post-polishing of `stagazer` output "
author: "Chandler Lutz"
date: "`r Sys.Date()`"
output: pdf_document
header-includes:
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{caption}
  - \floatplacement{figure}{H}   ##So figures get placed correctly in pdfs
  - \floatplacement{table}{H}   ##So figures get placed correctly in pdfs
  - \usepackage{setspace}
  - \onehalfspacing
urlcolor: blue

# Required: Vignette metadata for inclusion in a package.
vignette: >
  %\VignetteIndexEntry{starpolishr}
  %\VignetteKeywords{R,stargazer,latex,regression tables}
  %\VignetteDepends{starpolishr,stargazer,magrittr}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- css style for line spacing -->
<style type = "text/css">
p {
	line-height: 1.5;
}
</style>



First note that the first argument in all `starpolishr` functions is a
`stargazer` table, allowing for easy compatibility with
the
[magrittr](https://cran.r-project.org/web/packages/magrittr/index.html) `%>%`.
Also, all of the functions in the `starpolishr` package begin with
`star_` for easy `tab` completion in emacs or rstudio.

# Basic Stargazer Tables

To start, let's run a couple of regressions. These will be miles per
gallon, `mpg`, on `hp` and `cyl` from the `mtcars` dataset. We'll also
produce a
basic
[stargazer](https://cran.r-project.org/web/packages/stargazer/index.html) table.

```{r message=FALSE, results = 'asis'}
library(stargazer); library(starpolishr); library(magrittr)
data(mtcars)
mod.mtcars.1 <- lm(mpg ~ hp, mtcars)
mod.mtcars.2 <- lm(mpg ~ hp + cyl, mtcars)
star.out.1 <- stargazer(mod.mtcars.1, mod.mtcars.2,
                        title = "Motor Car Regressions",
                        type = "latex",
                        #For exact latex positioning using the latex 'float' package
                        table.placement = "H",
                        keep.stat = "n",
                        header = FALSE)
```


Obviously, a potential confound is the vehicle weight, `wt`. For the
purposes of this vignette, let's say we want the regressions that
employ the `wt` variable in a separate table:

```{r results = 'asis'}
#Second set of models with weight as a regressor
mod.mtcars.3 <- lm(mpg ~ hp + wt, mtcars)
mod.mtcars.4 <- lm(mpg ~ hp + cyl + wt, mtcars)
star.out.2 <- stargazer(mod.mtcars.3, mod.mtcars.4,
                        #For exact latex positioning using the latex 'float' package
                        table.placement = "H",
                        keep.stat = c("n", "rsq"),
                        header = FALSE)
```

# Updating Regression Variable Names

We can improve a number of things about these tables. First, the
left-hand and right-hand side variables are a bit cryptic. Let's clean
this up using `starpolishr` `star_lhs_names()` and `star_rhs_names()`
functions, which use regular expressions to replace variable
names. The advantage of these functions is that they allow the
variable names to span more than one line. As we want to apply these
functions to both tables, let's create a function to minimize
duplicative code.

```{r }
clean_var_names <- function(table) {
    table %>%
        #Update the RHS names
        star_rhs_names(pattern = c("hp", "cyl", "wt"),
                       line1 = c("Hoarsepower", "Number of", "Vehicle"),
                       line2 = c("", "Engine Cylinders", "Weight")) %>%
        star_lhs_names(pattern = c("mpg"),
                       line1 = "Miles per",
                       line2 = "Gallon")
}

```

Now let's apply the function to the two stargazer tables and print

```{r results = 'asis'}
star.out.1 <- clean_var_names(star.out.1)
star.out.2 <- clean_var_names(star.out.2)
```

```{r results = 'asis'}
cat(star.out.1)
```

```{r results = 'asis'}
cat(star.out.2)
```

\clearpage

# Create a table with 2 panels and add custom notes

Now let's combine the tables into a two panel single table using the
`star_panel()` function and add custom table notes using the
`star_notes_tex()` function. Finally, we'll print the output


```{r results='asis'}
star_panel(star.out.1, star.out.2,
           panel.names = c("Reg Without Weight", "Reg With Weight"),
           panel.label.fontface = "bold" #For bold panel names
           ) %>%
    #Add table notes
    star_notes_tex(note.type = "caption", #Use the latex 'caption' package for notes
                   note = "Standard errors are in parentheses") %>%
    cat
```

